Very simplified likelihood

### 2024-02-21 inst/very_simplified_likelihood.Rmd
bugfix

```{r usehyper3}
a <- seq(from=0,to=1,by=0.01)
fhyper3 <- function(r,n){
  out <- hyper3()
  out['a'] <- 1
  out['b'] <- r
  for(i in (n-r):n){
    out[c(a=1,b=i)] %<>% dec
  }
  return(out)
}

>>>>

```{r usehyper3}
n <- 7
a <- seq(from=0,to=1,by=0.01)
fhyper3 <- function(r,n){
  out <- hyper3()
  out['a'] <- 1
  out['b'] <- r
  for(i in (n-r):n){
    out[c(a=1,b=i)] %<>% dec
  }
  return(out)
}
